### 2013-05-15 context-dependence.tex
.

@@

>>>>

Review stats lit, e.g. reviews by Friel, original by Besag (autologistic model), genetics by Larribe and Fearnead.

@@

%%%%
\subsection{Poisson approximation?}

Now we know how to compute the (marginal) probability that a particular subsequence changes into another subsequence.
Therefore, if we know the pattern $x$ (say) appears $N(x)$ times in the original sequence $X(0)$,
the expected number of times $y$ would appear juxtaposed with $x$ is $N(x)p_{\ell,m,r}(x,y)$.

\begin{flushright}
\begin{tabular}{c|ccccccc}
 $X(0)$ &  C  & A & C & T & C & A & C \\
 $X(t)$ &  $\centerdot$  & $\centerdot$  & C & T & C & $\centerdot$  & $\centerdot$  
\end{tabular}
\end{flushright}

There is correlation, of course.
